Learning filters from markers

### 2020-03-12 egpaper_for_review.tex
describe method

Observe que a convolução em um spel $p \in D$ corresponde ao produto interno do vetor de carterísticas locais extendido e o vetor que representa o filtro. Dessa forma, seja $H$ um híperplano ortogonal ao vetor de uma filtro $\mF$. Esse hyperplano divide o espaço em três partes: os pontos de um lado do hyperplano, os pontos do outro lado e os pontos no hyperplano. Vetores parecidos com o vetor do filtro $\mF$ devem cair do mesmo lado do hiperplano que $\mF$. Ou seja, se o vetor $\E(p)$ está do mesmo lado de $H$ que $\mF$, entao o produto interno entre $\E(p)$ e $\mF$ é positivo, e é negativo caso contrário.

>>>>

Note that the convolution in a spel $p \in D$ corresponds to the doct product of the locally extended feature vecture and the vector that represents the filter. Thus, let $H$ be a hyperplane orthogonal to the vector of a $\mF$ filter. Thus, let $ H $ be a hyperplane orthogonal to the vector of a $ \mF$ filter. Vectors similar to the vector of filter $\mF$ must fall on the same side of the hyperplane as $\mF$. That is, if the vector $\E(p)$ is on the same side of $H$ as $\mF$, then the doct product between $\E (p)$ and $\mF$ is positive, and is negative otherwise. Thus, the doct product between the center of a cluster and each of the vectors of that cluster must be positive, which implies that the center is a good filter to identify the pattern described by that cluster. In the Figure (fazer a figura) we can see an example.

Since all the patches used to produce the filters are centered around the origin, as well as the images of $\D$, we have that the hyperplanes ortogonal to the filters contain the origin, therefor there is no need for bias.
